Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-10 paper/main.tex
cleaning todos2
some changes to report of group results

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{comment}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[disable]{todonotes}
% \usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
	colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

@@

\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: }

@@

\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard}

\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen}

@@

\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV.
Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because the
of blindly averaging the actual frame content in the categories of movie cuts
(cf. shortcomings); this ``cross-modal control things'' seems to more confuse
than having its merits}

@@

% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.
% what we did
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used simplified stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from a visual localizer experiment.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

% intro
First on a group average level, we tested if we could isolate the PPA using GLM
contrasts based on the audio-description's annotation of speech.
% primary AO contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom > all
non-geo}) yielded six significant clusters (see Table \ref{tab:res-ao-group1},
Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
specifically, the clusters of the current analysis are at the borders of the
posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
lingual gyrus.
% precuneus
Two additional clusters are located in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

% all eight AO PPA contrasts
In order to test the robustness of our findings, we created seven additional
$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
% results
Six of the overall eight AO contrasts show significant bilateral clusters in
anterior regions of the group PPA overlap (see Figure
\ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.
% question
\todo[inline]{concluding statement often feels like interpretation/discussion}
%
\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}

% figure group results of robustness across all AO & AV contrasts
\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA.
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}), both on top of the MNI152 T1-weighted head
        template (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).}
    \label{fig:stability-slices}
    \end{figure*}

\subsubsection{AO: other significant clusters across contrasts}
% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list; depends on the discussion I guess}
% ventral precuneus = retrosplenial cortex?
So far, just a short list => 7 contrasts: bilateral clusters in RSC (and ventral
precuneus);
% transverse occipital sulcus = occipital place area
6 contrasts (4 bilateral, 2 unilateral): lateral occipiatal cortex (transverse
occipital sulcus; occipiatal place area?; AO clusters are more lateral, AV
cluster are more medial (\& caudal) but AO \& AV clusters overlap)
% confounds
4 contrasts: right superior temporal gyrus (auditory cortices); 3 contrasts:
left superior temporal gyrus; 3 contrasts: some (smallish) prefrontal clusters

\subsubsection{AV: PPA in primary contrast}
% AV intro
Second as conceptual/cross-modal control of the group average results, we
analyzed data from the audio-visual movie by contrasting different kinds of
movie cuts independent(ly) from the frames' visual content following the cuts.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to an unfamiliar setting
with cuts within familiar setting (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises (reported from posterior to
anterior), parts of the intracalcarine and cuneal cortex, the lingual gyrus and
retrosplenial cortex, the occipital and temporal fusiform gyrus and the
parahippocampal cortex in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

\begin{table*}[t]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection{AV: other signficant clusters across contrasts}

@@

\todo[inline]{contrasts are mentioned in the method section for the purpose of
    completeness. Shall results be reported (and later discussed)? Following is
a short overview}

@@

% AV stimulus
AV stimulus. All contrasts using ``no cut condition'' > x yield null results.
The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
parietal lobe. Compate Figure \ref{fig:reg-corr}: nouns that cue change to a new
setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
second highest correlation of a verbal cue category with a cut category; AND:
nouns that cue change to a familiar setting are somewhat correlated with cuts to
a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
category with a cut category).

>>>>

\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{comment}
\usepackage{svg}
\usepackage{caption, booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2cm,right=4cm,top=2cm,bottom=2cm]{geometry}
\usepackage[
	colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{40pt}
\lhead{\textsc{\scidatalogo}}
\usepackage{natbib}

@@

\todo[inline]{most of phrases containing the word ``isolate'' is gone; doing the
    revision of the result section I realized that we probably should
    ``somehow'' add that clusters should not be all over the place but spatially
    constrained to the parahippocampal and neighbouring cortices, because
    naturalistic stimulus / possibly confounding variables}

@@

\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: yes,
maybe reference Sengupta who are interested in the details? en passant makes
more sense here imo}

@@

\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard; imo it is
important that we do not have clusters all over the brain}

\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
yes, I know it is kinda difficult, tried my best to choose/tweak the color map}

@@

\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV.
    Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because
    of blindly averaging the actual frame content in the categories of movie
    cuts (cf. methods/regressors, discussion/shortcomings); this ``cross-modal
    control things'' seems to more confuse than having its merits}

@@

\todo[inline]{following is one exemplary sentence that would benefit from also
mentioning that clusters should not be all over the brain which could be the
case because naturalistic paradigm / confounding variables etc.}

% study goal
The goal of this study was to investigate if cues about the spatial layout
embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was define by using a visual localizer experiment
within the same subjects \citep{sengupta2016extension}.
% what we did We
annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used conceptualized
stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from the visual localizer.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.\todo{``localization'' performance}
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

% intro
First on a group average level, we tested if results of a whole-brain analysis
based on the audio-description's annotation would lead to increased hemodynamic
activity in the PPA.
% primary AO contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, the clusters of the current analysis are at the borders of the
posterior parahippocampal cortex, the occipital and temporal fusiform gyrus and
lingual gyrus.
% precuneus
Two additional clusters are located in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

% all eight AO PPA contrasts
In order to test the robustness of our findings, we created overall eight
$t$-contrasts for the AO stimulus (see Table \ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.
% question
\todo[inline]{concluding statement often feels like interpretation/discussion}
%
\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}

% figure group results of robustness across all AO & AV contrasts
\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters (Z>3.4; p<.05, cluster corrected)
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}) that were used to [isolate] the PPA
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).}
    \label{fig:stability-slices}
    \end{figure*}

\paragraph{AO: other significant clusters across contrasts}
% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list; depends on the discussion I guess;
anyhow: clusters are not ``random'' but make sense which speaks for the use of
naturalistic stimuli}

\begin{itemize}
\item RSC (and ventral precuneus): 7 contrasts (all bilateral)
\item lateral occipiatal cortex: 6 contrasts (4 bilateral, 2 unilateral =
    transverse occipital sulcus / occipiatal place area?; AO \& AV clusters
    overlap but AO clusters are more lateral, AV cluster are more medial \&
    caudal)
\item right superior temporal gyrus (auditory cortices): 4 contrasts
\item (smallish) prefrontal clusters: 3 contrasts (non-overlapping)
\end{itemize}

\subsubsection{AV: PPA in primary contrast}
% AV intro
As conceptual/cross-modal control of the group average results, we also analyzed
data from the audio-visual movie by contrasting different kinds of movie cuts
independent(ly) from the frames' visual content following the cut.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to a recurring setting (\texttt{vse\_new > vpe\_old}) yielded
three significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises, parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex (left bigger than right).

\begin{table*}[t]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

@@

\paragraph{AV: other signficant clusters across contrasts}

\begin{itemize}
\item lateral occipital cortex: 4 contrasts (all bilateral)
\end{itemize}

@@

\todo[inline]{contrasts are mentioned in the method section for the purpose of
completeness. Shall results be reported (and later discussed)?}

@@

% AV stimulus
AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
parietal lobe. Compate Figure \ref{fig:reg-corr}: nouns that cue change to a new
setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
second highest correlation of a verbal cue category with a cut category; AND:
nouns that cue change to a familiar setting are somewhat correlated with cuts to
a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
category with a cut category).
